Scaffolder - Software for Reproducible Genome Scaffolding.

### 2011-03-07 src/article.tex
Add section on scaffolder input data and algorithm

>>>>

\subsection*{Input sequence data and scaffolding process} %{{{2

The input data for Scaffolder is nucleotide sequence in FASTA format file.
These nucleotide sequences can be of any length and for example may be
individual sequences, assembled contigs or contigs which have been joined to
into larger scaffolds. The case in which Scaffolder may be most useful is using
the contigs and scaffolded contigs produced from assembling a set of sequencing
reads. \pb

The scaffolder algorithm reads through the scaffolder file parsing each entry
in the file. Each entry is converted to corresponding sequence by fetching from
the FASTA file and then performing any designated sequence processing
operations. Each of the sequence entries are then joined as a s single super
sequence and returned to the console output. \pb
